INGRID: Creating Languages in MPS from ANTLR Grammars

### 2016-10-12 chapters/background.tex
minor changes

\paragraph{Structure.}
The fundamental aspect of any MPS language is Structure.
It must be created first for each intended element (concept) of the language.
Structure specifies core attributes of an MPS concept such as the name, inheritance relationships, possible child concepts (including their types and cardinalities), the implemented interfaces, and references to other AST nodes.
% other properties (fields of any type that can hold values), etc.
Figure~\ref{fig:if_statement_structure} shows definition of the Structure aspect for the \code{if-else} statement.
\PP{Mozna trochu vic popsat obsah figure --- co znamenaji jednotlive prvky definice.}

@@

Figure~\ref{fig:if_editor_definition} shows an example of what the definition of the Editor aspect for the \code{if-else} statement might look like.
While here we indicate positions of cell borders on each line by spaces (just for the purpose of illustration), MPS GUI actually uses a graphically much more appealing way of displaying the Editor aspects, which involves vertical and horizontal lines of different colors and also background colors other than white for some cells.
\PP{Vysvetlit symboly "[-", "-]" \%, a dalsi ktere nejsou hned zrejme.}

@@

This approach also has some downsides.
Because MPS doesn't offer any tools that would allow easy transformation from the MPS grammar to the MPS language, the second step of the import process hasn't been implemented yet and will be probably very problematic.
Another downside might be the need for a double transformation implementation -- first one being the import of the text grammar to the MPS grammar definition.

>>>>

\paragraph{Structure.}
The fundamental aspect of any MPS language is Structure.
It must be created first for each intended element (concept) of the language.
Structure specifies core attributes of an MPS concept such as the name, inheritance relationships, possible child concepts (including their types and cardinalities), the implemented interfaces, and references to other AST nodes.
% other properties (fields of any type that can hold values), etc.
Figure~\ref{fig:if_statement_structure} shows definition of the Structure aspect for the \code{if-else} statement.

@@

Figure~\ref{fig:if_editor_definition} shows an example of what the definition of the Editor aspect for the \code{if-else} statement might look like.
While here we indicate positions of cell borders on each line by spaces (just for the purpose of illustration), MPS GUI actually uses a graphically much more appealing way of displaying the Editor aspects, which involves vertical and horizontal lines of different colors and also background colors other than white for some cells.
The symbols \verb|[-| and \verb|-]| represent layout information (cells), such as indentation.

@@

This approach also has some downsides.
Because MPS doesn't offer any tools that would allow easy transformation from the MPS grammar \PP{To je konkretni gramatika zadefinovana pomoci MPS jazyka pro ANTLR} to the MPS language, the second step of the import process hasn't been implemented yet and will be probably very problematic.
Another downside might be the need for a double transformation implementation -- first one being the import of the text grammar to the MPS grammar definition.
